MulMeokNyang\\ {\footnotesize \textsuperscript{}Intelligent cat watering machine that Recognizes individual cats with AI}

### 2023-11-03 Documentation/paper.tex
added group name
modified email

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% Document Class: IEEEtran 2015/08/26 V1.8b by Michael Shell
% -- See the "IEEEtran_HOWTO" manual for usage information.
% -- http://www.michaelshell.org/tex/ieeetran/

% past year documentations for reference
% https://github.com/SWE-AIManager/document/blob/main/documentation/ai-jansori.pdf
% https://github.com/goodtho/WakeupBuddy/blob/main/Documentation/Documentation_WakeUpBuddy.pdf
% https://github.com/2021hyt6-techblog/se-paper/blob/main/RecyclingAssistant-Paper.tex

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{float}
\usepackage{filecontents}   
\usepackage{lipsum}
\begin{document}

@@

\author{\IEEEauthorblockN{Ann Jukyung}
\IEEEauthorblockA{\textit{Dept. Information Systems} \\
\textit{Hanyang University}\\
Seoul, South Korea \\
email@hanyang.ac.kr}
\and
\IEEEauthorblockN{Choi Chansol}
\IEEEauthorblockA{\textit{Dept. Information Systems} \\
\textit{Hanyang University}\\
Seoul, South Korea \\
email@gmail.com}
\and
\IEEEauthorblockN{Lee Yunsun}
\IEEEauthorblockA{\textit{Dept. Information Systems} \\
\textit{Hanyang University}\\
Seoul, South Korea \\
email@gmail.com}
\and
\IEEEauthorblockN{Hong JunGgi}
\IEEEauthorblockA{\textit{Dept. Information Systems} \\
\textit{Hanyang University}\\
Seoul, South Korea \\
sentorino@hanyang.ac.kr}
}

@@

\section{Role Assignment}
Roles are assigned to improve software development process and increase team productivity.
\newline

@@

\section{INTRODUCTION}
\subsection{Motivation}
Cats tend to consume only the least amount of water, and due to this lack of drinking water, they often have health problems and have to go to the hospital regularly. Since animals are not applied by insurance, the burden of owners is considerable. In addition, in order to increase the amount of water consumed, the owners make them drink wet feed or force them to drink water through injections, but some cats suffer from allergic reactions to wet feed, and they show severe rejection to forced water intake by injection. \\
So we need a natural way to increase the amount of water consumed. Also, the number of households raising companion animals is increasing these days due to the increase in single or two-person households. \\

@@

\section{REQUIREMENTS ANALYSIS}
\subsection{Sign up}
\begin{itemize}
\item{\emph{Basic Information Input Screen:}}
    \begin{itemize}
        \item Method 1) Quick Sign-Up Feature
        \begin{itemize}
            \item Utilizes the Kakao, Google, and Naver sign-up APIs.
            \item If a quick sign-up is done, it directly proceeds to the user profile setup screen.
        \end{itemize}
        \item Method 2) Local Sign-Up Feature
        \begin{itemize}
            \item Email Input: The system checks and displays whether the input is in the correct email format or if the email has already been registered.
            \item Password and Password Confirmation Input: The system checks if both values match and displays the result on the screen.
            \item Phone Number Input and Authentication: Uses the NICE mobile phone authentication API. Once the authentication is complete, it displays the result on the screen.
        \end{itemize}
        \item If all the fields are correctly filled out and authentication is complete, the "Next" button is activated, leading the user to the user profile setup screen. \newline 
    \end{itemize}
\item{\emph{User Profile Setup Screen:}}
    \begin{itemize}
        \item Profile Picture Registration (optional)
            \begin{itemize}
            \item Clicking the "Add Photo" button allows the user to either fetch a photo from the album or take one instantly with the camera. The chosen photo can then be registered.
            \item If no photo is registered separately, a default image is displayed. - Nickname Input (Required)
            \end{itemize}
        \item Nickname Input (Required)
            \begin{itemize}
            \item The system checks the format and checks for duplicates, then displays the result on the screen.
            \end{itemize}
        \item Self-Introduction Input (optional)
            \begin{itemize}
            \item A maximum character count is specified.
            \end{itemize}
        \item If the nickname is correctly entered, the "Complete Sign-Up" button is activated. After sign-up, the user starts from the <water dispenser device registration> screen in a logged-in state and proceeds through the cat hydration management space creation procedure.\\
    \end{itemize}
\end{itemize}

@@

\subsection{Find Email}
\begin{itemize}
\item First, authenticate the user using the NICE Mobile Phone Verification API.
\item Upon successful authentication, the system searches the database using the phone number and displays the user's email on the screen.\\
\end{itemize}

@@

\subsection{Cat Hydration Management Space (Main)}
\subsubsection{Daily Hydration Info for Each Cat}
\begin{itemize}
    \item Cat Profile Selection Top Bar
    \begin{itemize}
        \item By tapping the profile picture, users can access the hydration info screen for that specific cat.
    \end{itemize}
    \item Cat Profile
    \begin{itemize}
        \item Displays the cat's profile picture, name, age, and weight.
        \item An edit button lets users access a screen where they can modify that cat's profile. (Reuses the Cat Profile Registration screen).
        \item Tapping the right arrow displays the daily hydration info for the next cat. The last item is a plus button, which leads to a screen to add a new cat profile. (Reuses the Cat Profile Registration screen).
    \end{itemize}
    \item Daily Hydration Gauge
    \begin{itemize}
        \item Displays how much of the daily hydration goal the cat has achieved, as a percentage(\%).
        \item Different colors indicate hydration ranges:
        \begin{itemize}
            \item 0\% ~ 29\%: Red
            \item 30\% ~ 59\%: Yellow
            \item 60\% ~ 89\%: Green
            \item 90\% ~ Upper Limit: Blue
            \item Upper Limit ~ 200\%: Blue up to the upper limit, then red
        \end{itemize}
        \item The upper limit is set to address excessive hydration, calculated using the recommended formula.
        \item Push notifications are sent to the user if the upper limit is exceeded.
    \end{itemize}
    \item Daily Hydration Evaluation \& Advice
    \begin{itemize}
        \item Based on the cat's water intake for the day, an evaluation is given, advising if more water intake is needed.
    \end{itemize}
    \item Hydration Statistics Button
    \begin{itemize}
        \item Leads to the periodical hydration statistics screen for that cat.
    \end{itemize}
    \item Watering Attempt Button
    \begin{itemize}
        \item Tapping this button prompts the water dispenser to make a cat-calling sound, enticing the cat to approach and drink.
        \item If the cat drinks within 30 minutes, a push notification is sent to the user.
    \end{itemize}
    \item Navigation Bar
    \begin{itemize}
        \item Tapping the NavigationBarIcon slides out the navigation bar from the left.\\
    \end{itemize}
\end{itemize}
\subsubsection{Periodical Hydration Statistics Screen}
\begin{itemize}
    \item Cat Profile Selection Top Bar
    \begin{itemize}
        \item If accessed from a specific cat's daily hydration info screen, that cat is selected.
        \item Otherwise, the first cat is selected by default.
        \item Users can view statistics for other cats by selecting their profiles.
    \end{itemize}
    \item By default, displays a bar graph of the past week's hydration data.
    \item Users can choose between 'One Week/One Month/One Year' durations.
    \item A calendar button allows users to select specific 'Week/Month/Year'.
    \item Tapping a bar displays hydration data for that specific 'Day/Week/Month'.
    \begin{itemize}
        \item If the graph is set for one week, it displays data for that day.
        \item If set for one month, it displays data for that week.
        \item If set for one year, it displays data for that month.
    \end{itemize}
    \item At the bottom, an evaluation and advice on hydration are provided.
    \begin{itemize}
        \item If 'Red' or 'Yellow' days make up more than half, a message suggests increasing water intake.
        \item If 'Green' or 'Blue' days make up more than half, a message confirms adequate hydration.
        \item If days with 'Blue + Red' make up more than half, a message advises consulting with a veterinarian due to excessive water intake.\\
    \end{itemize}
\end{itemize}

@@

\newpage
\section{TASK DISTRIBUTION}
% add description if needed
\begin{table}[!htbp]\normalsize
\begin{center}
\begin{tabular}{|p{1.2cm}|p{1.9cm}|p{4.5cm}|}
\hline
\textbf{Name} & \textbf{\textit{Role}}& \textbf{\textit{Responsibilities}}\\
\hline
Choi Chansol & Front-end &
The role involves developing mobile apps for Android and iOS using React Native. It includes UI/UX design, feature integration, and communication with the backend server via RESTful API for seamless functionality.
\\ \hline
Ann Jukyung \& Lee Yunsun & Back-end &
The responsibilities for this role encompass various aspects of software development and database management. This includes database design and management, which involves overseeing and organizing user information, device information, and statistical data. Additionally, this position involves server-client communication, and it specifically utilizes Node.js for this purpose. In terms of development frameworks, it relies on Express.js. The chosen database environment is AWS with MySQL. This multifaceted role entails not only creating and managing the database structure but also maintaining efficient server-client communication for a seamless and responsive user experience.
\\ \hline
\end{tabular}
\label{tab1}
\end{center}
\end{table}
\newpage
\begin{table}[!htbp]\normalsize
\begin{center}
\begin{tabular}{|p{1.2cm}|p{1.9cm}|p{4.5cm}|}
\hline
Hong Jun Ggi & AI &
The development environment for this project comprises Python 3.11 within a WSL (Windows Subsystem for Linux) setup. The core objective involves individual cat recognition based on unique nose prints. To achieve this, various libraries are employed, including OpenCV 4 for image processing and the likely integration of scikit-learn (sklearn) for machine learning capabilities. Additionally, for data visualization and analysis, visualization libraries like Matplotlib are utilized. Furthermore, the project explores the realm of generative AI (OpenAI API), possibly in collaboration with SKT NUGU, to enhance its capabilities and further its objectives.
\\ \hline
\end{tabular}
\label{tab2}
\end{center}
\end{table}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% Document Class: IEEEtran 2015/08/26 V1.8b by Michael Shell
% -- http://www.michaelshell.org/tex/ieeetran/

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{float}
\usepackage{filecontents}
\usepackage{kotex}
\usepackage{lipsum}

\documentclass{scrreprt}
\makeatletter
\usepackage{color}
\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
\definecolor{orange}{rgb}{1,0.45,0.13}		
\definecolor{olive}{rgb}{0.17,0.59,0.20}
\definecolor{brown}{rgb}{0.69,0.31,0.31}
\definecolor{purple}{rgb}{0.38,0.18,0.81}
\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
\definecolor{lightred}{rgb}{1,0.4,0.5}
\usepackage{upquote}
\usepackage{listings}
% CSS
\lstdefinelanguage{CSS}{
  keywords={color,background-image:,margin,padding,font,weight,display,position,top,left,right,bottom,list,style,border,size,white,space,min,width, transition:, transform:, transition-property, transition-duration, transition-timing-function},	
  sensitive=true,
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]",
  alsoletter={:},
  alsodigit={-}
}

% JavaScript
\lstdefinelanguage{JavaScript}{
  morekeywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
  morecomment=[s]{/*}{*/},
  morecomment=[l]//,
  morestring=[b]",
  morestring=[b]'
}

\lstdefinelanguage{HTML5}{
  language=html,
  sensitive=true,	
  alsoletter={<>=-},	
  morecomment=[s]{<!-}{-->},
  tag=[s],
  otherkeywords={
  % General
  >,
  % Standard tags
	<!DOCTYPE,
  </html, <html, <head, <title, </title, <style, </style, <link, </head, <meta, />,
	% body
	</body, <body,
	% Divs
	</div, <div, </div>, 
	% Paragraphs
	</p, <p, </p>,
	% scripts
	</script, <script,
  % More tags...
  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
  },
  ndkeywords={
  % General
  =,
  % HTML attributes
  charset=, src=, id=, width=, height=, style=, type=, rel=, href=,
  % SVG attributes
  fill=, attributeName=, begin=, dur=, from=, to=, poster=, controls=, x=, y=, repeatCount=, xlink:href=,
  % properties
  margin:, padding:, background-image:, border:, top:, left:, position:, width:, height:, margin-top:, margin-bottom:, font-size:, line-height:,
	% CSS3 properties
  transform:, -moz-transform:, -webkit-transform:,
  animation:, -webkit-animation:,
  transition:,  transition-duration:, transition-property:, transition-timing-function:,
  }
}

\lstdefinestyle{htmlcssjs} {%
  % General design
%  backgroundcolor=\color{editorGray},
  basicstyle={\footnotesize\ttfamily},   
  frame=b,
  % line-numbers
  xleftmargin={0.75cm},
  numbers=left,
  stepnumber=1,
  firstnumber=1,
  numberfirstline=true,	
  % Code design
  identifierstyle=\color{black},
  keywordstyle=\color{blue}\bfseries,
  ndkeywordstyle=\color{editorGreen}\bfseries,
  stringstyle=\color{editorOcher}\ttfamily,
  commentstyle=\color{brown}\ttfamily,
  % Code
  language=HTML5,
  alsolanguage=JavaScript,
  alsodigit={.:;},	
  tabsize=2,
  showtabs=false,
  showspaces=false,
  showstringspaces=false,
  extendedchars=true,
  breaklines=true,
  % German umlauts
  literate=%
  {Ö}{{\"O}}1
  {Ä}{{\"A}}1
  {Ü}{{\"U}}1
  {ß}{{\ss}}1
  {ü}{{\"u}}1
  {ä}{{\"a}}1
  {ö}{{\"o}}1
}
%
\lstdefinestyle{py} {%
language=python,
literate=%
*{0}{{{\color{lightred}0}}}1
{1}{{{\color{lightred}1}}}1
{2}{{{\color{lightred}2}}}1
{3}{{{\color{lightred}3}}}1
{4}{{{\color{lightred}4}}}1
{5}{{{\color{lightred}5}}}1
{6}{{{\color{lightred}6}}}1
{7}{{{\color{lightred}7}}}1
{8}{{{\color{lightred}8}}}1
{9}{{{\color{lightred}9}}}1,
basicstyle=\footnotesize\ttfamily, % Standardschrift
numbers=left,               % Ort der Zeilennummern
%numberstyle=\tiny,          % Stil der Zeilennummern
%stepnumber=2,               % Abstand zwischen den Zeilennummern
numbersep=5pt,              % Abstand der Nummern zum Text
tabsize=4,                  % Groesse von Tabs
extendedchars=true,         %
breaklines=true,            % Zeilen werden Umgebrochen
keywordstyle=\color{blue}\bfseries,
frame=b,
commentstyle=\color{brown}\itshape,
stringstyle=\color{editorOcher}\ttfamily, % Farbe der String
showspaces=false,           % Leerzeichen anzeigen ?
showtabs=false,             % Tabs anzeigen ?
xleftmargin=17pt,
framexleftmargin=17pt,
framexrightmargin=5pt,
framexbottommargin=4pt,
%backgroundcolor=\color{lightgray},
showstringspaces=false,      % Leerzeichen in Strings anzeigen ?
}%
%
\makeatother

\begin{document}

@@

\author{\IEEEauthorblockN{Ann Jukyung}
\IEEEauthorblockA{\textit{Dept. Information Systems} \\
\textit{Hanyang University}\\
Seoul, South Korea \\
email@hanyang.ac.kr}
\and
\IEEEauthorblockN{Choi Chansol}
\IEEEauthorblockA{\textit{Dept. Information Systems} \\
\textit{Hanyang University}\\
Seoul, South Korea \\
email@hanyang.ac.kr}
\and
\IEEEauthorblockN{Lee Yunsun}
\IEEEauthorblockA{\textit{Dept. Information Systems} \\
\textit{Hanyang University}\\
Seoul, South Korea \\
email@hanyang.ac.kr}
\and
\IEEEauthorblockN{Hong JunGgi}
\IEEEauthorblockA{\textit{Dept. Information Systems} \\
\textit{Hanyang University}\\
Seoul, South Korea \\
sentorino@hanyang.ac.kr}
}

@@

\section{Role Assignment}
Roles are assigned to improve software development process and increase team productivity. Group name is called Nyangporter.
\newline

@@

\section{INTRODUCTION}
\subsection{Motivation}

Cats tend to consume only the least amount of water, and due to this lack of drinking water, they often have health problems and have to go to the hospital regularly. Since animals are not applied by insurance, the burden of owners is considerable. In addition, in order to increase the amount of water consumed, the owners make them drink wet feed or force them to drink water through injections, but some cats suffer from allergic reactions to wet feed, and they show severe rejection to forced water intake by injection. \\
So we need a natural way to increase the amount of water consumed. Also, the number of households raising companion animals is increasing these days due to the increase in single or two-person households. \\

@@

\section{REQUIREMENTS ANALYSIS}
\subsection{Sign up}
\begin{itemize}
\item{\emph{Basic Information Input Screen:}}
    \begin{itemize}
        \item Method 1) Quick Sign-Up Feature
        \begin{itemize}
            \item Utilizes the Kakao, Google, and Naver sign-up APIs.
            \item If a quick sign-up is done, it directly proceeds to the user profile setup screen.
        \end{itemize}
        \item Method 2) Local Sign-Up Feature
        \begin{itemize}
            \item Email Input: The system checks and displays whether the input is in the correct email format or if the email has already been registered.
            \item Password and Password Confirmation Input: The system checks if both values match and displays the result on the screen.
            % \item Phone Number Input and Authentication: Uses the NICE mobile phone authentication API. Once the authentication is complete, it displays the result on the screen.
        \end{itemize}
        \item If all the fields are correctly filled out and authentication is complete, the "Next" button is activated, leading the user to the user profile setup screen. \newline 
    \end{itemize}
\item{\emph{User Profile Setup Screen:}}
    \begin{itemize}
        \item Profile Picture Registration (optional)
            \begin{itemize}
            \item Clicking the "Add Photo" button allows the user to either fetch a photo from the album or take one instantly with the camera. The chosen photo can then be registered.
            \item If no photo is registered separately, a default image is displayed. - Nickname Input (Required)
            \end{itemize}
        \item Nickname Input (Required)
            \begin{itemize}
            \item The system checks the format and checks for duplicates, then displays the result on the screen.
            \end{itemize}
        \item Self-Introduction Input (optional)
            \begin{itemize}
            \item A maximum character count is specified.
            \end{itemize}
        \item If the nickname is correctly entered, the "Complete Sign-Up" button is activated. After sign-up, the user starts from the <water dispenser device registration> screen in a logged-in state and proceeds through the cat hydration management space creation procedure.\\
    \end{itemize}
\end{itemize}

@@

\subsection{Find Email}
\begin{itemize}
% \item First, authenticate the user using the NICE Mobile Phone Verification API.
\item Upon successful authentication, the system searches the database using the phone number and displays the user's email on the screen.\\
\end{itemize}

@@

\subsection{Cat Hydration Management Space (Main)}
\subsubsection{Daily Hydration Info for Each Cat}
\begin{itemize}
    \item Cat Profile Selection Top Bar
    \begin{itemize}
        \item By tapping the profile picture, users can access the hydration info screen for that specific cat.
    \end{itemize}
    \item Cat Profile
    \begin{itemize}
        \item Displays the cat's profile picture, name, age, and weight.
        \item An edit button lets users access a screen where they can modify that cat's profile. (Reuses the Cat Profile Registration screen).
        \item Tapping the right arrow displays the daily hydration info for the next cat. The last item is a plus button, which leads to a screen to add a new cat profile. (Reuses the Cat Profile Registration screen).
    \end{itemize}
    \item Daily Hydration Gauge
    \begin{itemize}
        \item Displays how much of the daily hydration goal the cat has achieved, as a percentage(\%).
        \item Different colors indicate hydration ranges:
        \begin{itemize}
            \item 0\% ~ 29\%: Red
            \item 30\% ~ 59\%: Yellow2
            \item 60\% ~ 89\%: Green
            \item 90\% ~ Upper Limit: Blue
            \item Upper Limit ~ 200\%: Blue up to the upper limit, then red
        \end{itemize}
        \item The upper limit is set to address excessive hydration, calculated using the recommended formula.
        \item Push notifications are sent to the user if the upper limit is exceeded.
    \end{itemize}
    \item Daily Hydration Evaluation \& Advice
    \begin{itemize}
        \item Based on the cat's water intake for the day, an evaluation is given, advising if more water intake is needed.
    \end{itemize}
    \item Hydration Statistics Button
    \begin{itemize}
        \item Leads to the periodical hydration statistics screen for that cat.
    \end{itemize}
    \item Watering Attempt Button
    \begin{itemize}
        \item Tapping this button prompts the water dispenser to make a cat-calling sound, enticing the cat to approach and drink.
        \item If the cat drinks within 30 minutes, a push notification is sent to the user.
    \end{itemize}
    \item Navigation Bar
    \begin{itemize}
        \item Tapping the NavigationBarIcon slides out the navigation bar from the left.\\
    \end{itemize}
\end{itemize}
\subsubsection{Periodical Hydration Statistics Screen}
\begin{itemize}
    \item Cat Profile Selection Top Bar
    \begin{itemize}
        \item If accessed from a specific cat's daily hydration info screen, that cat is selected.
        \item Otherwise, the first cat is selected by default.
        \item Users can view statistics for other cats by selecting their profiles.
    \end{itemize}
    \item By default, displays a bar graph of the past week's hydration data.
    \item Users can choose between 'One Week/One Month/One Year' durations.
    \item A calendar button allows users to select specific 'Week/Month/Year'.
    \item Tapping a bar displays hydration data for that specific 'Day/Week/Month'.
    \begin{itemize}
        \item If the graph is set for one week, it displays data for that day.
        \item If set for one month, it displays data for that week.
        \item If set for one year, it displays data for that month.
    \end{itemize}
    \item At the bottom, an evaluation and advice on hydration are provided.
    \begin{itemize}
        \item If 'Red' or 'Yellow' days make up more than half, a message suggests increasing water intake.
        \item If 'Green' or 'Blue' days make up more than half, a message confirms adequate hydration.
        \item If days with 'Blue + Red' make up more than half, a message advises consulting with a veterinarian due to excessive water intake.\\
    \end{itemize}
\end{itemize}

@@

\newpage
\section{Development Environment}
% add description if needed
\subsection{Choice of software development platform}
We are using windows 11 environment, we are likely to use bash terminal or WSL most of the time. Other tools like vscode or jupyter notebook will be based on windows 11. Windows might not be the best choice for software development environment but it is considered one of the good option and we don't have linux machine so we had no choice. In addition, Visual Studio Code will be used as IDE, and Typescript, Python, and MySQL will be used as languages.

\begin{table}[!htbp]\normalsize
\begin{center}
\begin{tabular}{|p{1.4cm}|p{6.2cm}|}
\hline
\textbf{Tool and language} & \textbf{\textit{Reason}}\\
\hline
Typescript & Typescript is an open-source programming language that is a super-set of JavaScript. By specifying the static type, type errors can be prevented, high code readability, and errors can be checked during compilation. It is also a class-based object-oriented programming language that can support inheritance, encapsulation, and generator. Since all the team members are familiar with JavaScript, and Typescript is a complementary language to JavaScript, we chose to learn it through this opportunity 
\\ \hline
React Native & React Native can develop platform applications and is partially compatible native. It was judged that developing Android and IOS applications in native languages was less efficient, and the accessibility of developing React Native was high due to the knowledge of React. In addition, it is a framework that is widely used in the field, so we chose it as the front-end language.
\\ \hline
Expo & Expo is a React Native cross platform for development. It was judged that Xcode was not available because we do not have a Mac OS device, and it was inefficient because it was not suitable for the project size to develop using both Android studio and Xcode. With Expo, IOS applications can be developed in Windows as well, and real-time tests can be made with mobile devices held through the Expo application. In addition, it was used because the initial setting was simple and there were many modules needed to develop the Expo SDK.
\\ \hline
\end{tabular}
\label{tab1}
\end{center}
\end{table}
\newpage

\begin{table}[!htbp]\normalsize
\begin{center}
\begin{tabular}{|p{1.8cm}|p{5.8cm}|}
\hline
Node.js & Node.js is commonly used by back-end development beginners because it can quickly process data with an asynchronous event-based architecture and provides most of what is needed in package manager. Most of the team members does not have back-end development experience and have knowledge of JavaScript, so we decide to use Node.js. Using Nest.js that supports Typescript as a framework, we hope to facilitate co-working with front-end developers who use React Native.
\\ \hline
MySQL & We need a database to store the user information, user's cat information, list of co-manager, and water consumption data. MySQL is an open-source relational database system language, we decide to use because all team members have used it in the "Database System" class.
\\ \hline
Amazon Web Services(AWS) & To back up and manage databases by building and hosting cloud-based servers, we intend to use Amazon Relational Database Service (RDS) and Amazon SageMaker to manage machine learning services. With SageMaker, data scientists and developers can quickly and easily build and train machine learning models, and then directly deploy them into a production-ready hosted environment. We can get a 12-month Free Tier also a reason for choice.
\\ \hline
Python 3.11 & Python is an interpreted, object-oriented, high-level programming language with dynamic semantics. Because Python is simple to use and it can be used in Machine Learning development, its popularity in AI and ML development is very high. We will be using libraries like matplotlib for visualization, tensorflow/pytorch for image classification, scikit-learn for data analysis, and all the rest of the necessary libraries like pandas or numpy etc.
\\ \hline
\end{tabular}
\label{tab1}
\end{center}
\end{table}
\textit{Cost Estimation}
\newline
We will use open source if possible, and servers will also use AWS Free Tier plans to avoid incurring development costs.
\newline
\subsection{Software in use}
\begin{itemize}
\item[a.]{\emph{Visual Studio Code(1.83.1)}}
   \newline
   Visual Studio Code (VSCode) is an open-source IDE and can be used in various environments such as Windows, macOS, and Linux. In addition to code editing, it supports various development tasks such as debugging, version management, and terminal access, also there are many extension plug-ins that can increase development productivity with plug-ins such as Prettiers. We chose this IDE because the OS of laptops used by team members is different, also it would be easy for everyone to use the same IDE for smooth cooperative working.
    \\ \end{itemize}
\begin{itemize}
\item[b.]{\emph{SKT NUGU}}
   \newline
   SKT NUGU is an artificial intelligence(AI) service based on voice recognition. It was intended to increase the user's convenience by notifying the amount of water consumption of cats through the voice of the water supplier even without accessing the application. SKT NUGU has the advantage of providing guidelines for developers to utilize, allowing them to mount artificial intelligence-based functions easily and quickly, and being able to test without NUGU devices in a GUI environment called Play Builder.
   \\ \end{itemize}
\begin{itemize}
\item[c.]{\emph{Git hub}}
   \newline
   A version management system based on Git that allows multiple developers to work simultaneously, track changes, and avoid conflicts. The remote storage provided enables collaboration online, and facilitates communication between team members, code review, and issue management. We hope to use GitHub to prevent version problems during collaboration and to check and develop each other's code.
    \\ \end{itemize}
\begin{itemize}
\item[d.]{\emph{Database Management System}}
   \newline
   A database management system is essential to manage the information of the user, the user's cats, and cats’ water consumption data. To easily and securely store the information associated with it, the database needs to be designed and built.
    \\ \end{itemize}
\begin{itemize}
\item[e.]{\emph{Figma}}
   \newline
   Figma is a web-based UI/UX design tool. It supports many designers and developers to collaborate in real-time, and does not require installation. It is easy to build and manage reusable components, making it possible to maintain a consistent design pattern, which also contributes to increasing developer productivity. In addition, it is available for free and is not difficult to use, so we chose it as a software design tool.
    \\ \end{itemize}
\begin{itemize}
\item[f.]{\emph{Open CV}}
   \newline
   This is a library of programming functions mainly for real-time computer vision. We found other alternatives like YOLOv8. However, it is unclear whether it could be used or not due to my limitation on knowledge and time. For now, we are looking to use built-in Haar Cascade alorithm for object detection.
    \\ \end{itemize}

\newpage
\subsection{Task distribution}
\begin{table}[!htbp]\normalsize
\begin{center}
\begin{tabular}{|p{1.2cm}|p{1.9cm}|p{4.5cm}|}
\hline
\textbf{Name} & \textbf{\textit{Role}}& \textbf{\textit{Responsibilities}}\\
\hline
Choi Chansol & Front-end &
The role involves developing mobile apps for Android and iOS using React Native. It includes UI/UX design, feature integration, and communication with the backend server via RESTful API for seamless functionality.
\\ \hline
Ann Jukyung \& Lee Yunsun & Back-end &
The responsibilities for this role encompass various aspects of software development and database management. This includes database design and management, which involves overseeing and organizing user information, device information, and statistical data. Additionally, this position involves server-client communication. This multifaceted role entails not only creating and managing the database structure but also maintaining efficient server-client communication for a seamless and responsive user experience.
\\ \hline
Hong Jun Ggi & AI &
The development environment for this project comprises Python 3.11 within a WSL (Windows Subsystem for Linux) setup. The core objective involves individual cat recognition based on unique nose prints. To achieve this, various libraries are employed, including OpenCV 4 for image processing and the likely integration of scikit-learn (sklearn) for machine learning capabilities. Additionally, for data visualization and analysis, visualization libraries like Matplotlib are utilized. Furthermore, the project explores the realm of generative AI (OpenAI API), possibly in collaboration with SKT NUGU, to enhance its capabilities and further its objectives.
\\ \hline
\end{tabular}
\label{tab2}
\end{center}
\end{table}

\section{SPECIFICATIONS}
\subsection{Database Structure}
The list below is the tables and schemes for MulMeokNyang database. When creating tables that need to be created in advance and cat's drink measurement management spaces, there are tables that need to be created dynamically.   \\

Tables that need to be generated in advance include a user table to store data for membership users and a session table to store data related to the automatic login function. \\

Tables that need to be dynamically generated include a management\_space table to store basic data related to management space, a cat\_in\_management\_space table to store basic data for cats to manage in management space, and a cat\_hydration\_statistics table to store data related to the drinking volume of a specific cat. Tables that need to be created dynamically are created together sequentially, and the table name includes the values of the spaceId and catId variables. This allows you to dynamically create and associate tables by management space and individual cat. \\

\subsubsection{Lists of tables that must be created in advance}
\begin{itemize}
    \item user table
    \begin{itemize}
        \item user\_email : primary key, not null, unique
        \item user\_pw : not null
        \item user\_name : not null
        \item user\_phonenum : not null, unique
        \item user\_profile\_photo
        \item user\_nickname : not null, unique
        \item user\_introduction
        \item management\_space\_id : default ‘’(Empty String)
    \end{itemize}
    \item session table
    \begin{itemize}
        \item session\_id : primary key, not null, unique
        \item user\_email : foreign key, not null, unique\\
    \end{itemize}
\end{itemize}
\subsubsection{Lists of tables that are going to be created statically}
\begin{itemize}
    \item management\_space\_\$\{spaceId\} table
    \begin{itemize}
        \item management\_space\_id : primary key, default \$\{spaceId\}
        \item main\_manager\_user\_email : foreign key, not null
        \item co\_managers\_user\_email : JSON, default ‘\{\}’
    \end{itemize}
    \item cat\_in\_management\_space\_\$\{spaceId\} table
    \begin{itemize}
        \item session\_id : primary key, not null, unique
        \item cat\_id : primary key, auto\_increment, default 0
        \item cat\_profile\_photo : not null
        \item cat\_name : not null
        \item cat\_age : not null
        \item cat\_weight : not null
        \item cat\_photos : JSON, default ‘\{\}’
        \item cat\_feedstuff\_daily\_consumption : not null
        \item cat\_feedstuff\_moisture\_content : not null88
        \item is\_hydration\_auto : not null
        \item cat\_goal\_hydration : not null
    \end{itemize}
    \item cat\_hydration\_statistics\_\$\{catId\} table
    \begin{itemize}
        \item date : primary key, CURDATE()
        \item day : default DAYOFWEEK(NOW())
        \item goal\_hydration : not null
        \item actual\_hydration : default 0
        \item hydration\_guage : default 0
    \end{itemize}
\end{itemize}

\subsection{Navigation}
In our application, it uses the Navigation module from the react-navigation package. \\

\subsubsection{Main Navigation}
\begin{itemize}
    \item Route List
    \begin{itemize}
        \item Start
        \item Login
        \item LocalSignUp
        \item UserProfileRegistration
        \item Find
        \begin{itemize}
            \item FindEmail
            \item FindEmailResult
            \item FindPw
        \end{itemize}
        \item HowToGoSpace
        \item PendingCoManagerAddition
        \item DeviceRegistration
        \item CatInfoRegistration
        \begin{itemize}
            \item CatProfileRegistration
            \item CatPhotosRegistration
            \item CatFeedStuffRegistration
            \item CatHydrationRegistration
        \end{itemize}
        \item Main
        \item HydrationStatistics \\
    \end{itemize}
\end{itemize}

\subsubsection{Drawer Navigation}
\begin{itemize}
    \item Route List
    \begin{itemize}
        \item UserProfileModification
        \item CatInfoRegistration
        \begin{itemize}
            \item CatProfileRegistration
            \item CatPhotosRegistration
            \item CatFeedStuffRegistration
            \item CatHydrationRegistration
        \end{itemize}
        \item CatInfoModification
        \begin{itemize}
            \item CatProfileModification
            \item CatFeedStuffModification
            \item CatHydrationModification
        \end{itemize}
        \item CoManagerSet \\
    \end{itemize}
\end{itemize}

\subsection{Frequently Used Custom Component}
The following five Component are Custom Component used throughout our application. \\

\subsubsection{TopBar Component}
\begin{itemize}
    \item[] \includegraphics[width=0.3\textwidth]{img/C/1.png}
    \item The title of the current screen appears in the center, and depending on what the current screen is, go back icon and menu icon are visible.
    \item It's also used in Drawer Navigation, where it turns into a close icon rather than a backward one. \\
\end{itemize}

\subsubsection{InputContainer Component}
\begin{itemize}
    \item[] \includegraphics[width=0.27\textwidth]{img/C/2.png}
    \item Used on the Login, Sign Up, and Information Registration page.
    \item The title on the top of the page represents what that input page is for and if input requirement is not satisfied, msg will deliver information on how to satisfy those input requirements.
    \item Input values such as password and password verification are made invisible.
    \item If the input window requires a unit, the unit is shown on the right.
    \item On each screen, it passes the required validation function to properly proceed with the validation. If the validation fails, the form submit button is not activated. \\
\end{itemize}

\subsubsection{Button Component}
\begin{itemize}
    \item[] \includegraphics[width=0.25\textwidth]{img/C/3.png}
    \item Title appear and indicate which button this is inside the button.
    \item Pressing the button changes the color to navy.
    \item When it is triggered by Alert Component, it replaces the border raidus to 0.
    \item The button type includes a button to move to the specific page and a button to select a value. This is distinguished by passing the goRoute for screen movement in method property and the selectOpt value for value selection.\\
\end{itemize}
